### 2023-10-14 chapters/paper_review/04_benchmarking.tex
Fix many spelling and language errors

\subsection{Datasets only for pre"=training} 
\Cref{table:datasets} summarizes datasets used for pre"=training SSL techniques
in the literature. These datasets are usually large but with limited or no
labels. Libri-light (LL)~\parencite{kahn_libri-light_2020}, one of these datasets, is
derived from audiobooks that are part of the
LibriVox\footnote{https://librivox.org/ \label{librivox}} project. LL contains
60k hours of spoken English audio tagged with SNR, speaker ID, and genre
descriptions. The speech examples in Audioset~\parencite{gemmeke_audio_2017}, which
consists of over 2M 10-second YouTube video clips human-annotated with 632
audio events, have also been used for pre"=training. Audioset has 2.5k hours
of audio of varying quality, different languages, and sometimes multiple sound
sources. AVSpeech~\parencite{ephrat_looking_2018} is another large-scale audio-visual
dataset used in SSL research, comprising 4.7k hours of clips from a wide
variety of languages. 
Each clip contains a visible face and audible sound originating from a single
speaker without interfering background signals. The 3100-hour audio part of
AVSpeech has been used to learn audio-only 
representations~\parencite{kawakami_learning_2020}. The Fisher corpus~\parencite{cieri_fisher_2004} collects
over 2k hours of conversational telephone speech, 1k hours of which is utilized
for pre"=training~\parencite{jiang_further_2021}. Industrial researchers have also
begun to build large-scale datasets for learning speech representations.
For instance, 10k hours of real-world far-field English voice commands for
self"=supervised pre"=training have been collected at 
Amazon~\parencite{sadhu_wav2vecc_2021}.

In addition to these English and multilingual efforts, researchers have also
collected corpora for pre"=training Chinese speech representations. Didi Dictation
and Didi Callcenter~\parencite{jiang_improving_2019, jiang_further_2021} are two
internal datasets containing respectively 10k hours of read speech collected
from mobile dictation application and 10k hours of spontaneous phone calls
between users and customer service staff.

@@

The speech community also utilizes multilingual corpora. These are often
large-scale, which facilitates pre"=training, but are also partially labeled for ASR
evaluation (PC and PR can be enabled via phone-level forced alignment). These
corpora include Common Voice (CV)~\parencite{ardila_common_2020}, Multilingual
LibriSpeech (MLS)~\parencite{pratap_mls_2020}, VoxPopuli 
(VP)~\parencite{wang_voxpopuli_2021}, and BABEL (BBL)~\parencite{gales_speech_2014}. CV is
an open-source, multi-language, growing dataset of voices containing 11k hours
of audio from 76 languages as of the date this review was written (Common Voice
corpus~7.0). Researchers usually use part of this for pre"=training (e.g., 7k
hours/60 languages in \parencite{babu_xlsr_2021} and 430 hours/29 languages in
\parencite{kawakami_learning_2020}) or evaluation. 
MLS derives content from read audiobooks of LibriVox and contains data in eight
European languages for a total of 50k hours of audio. VP comprises a total of 400k
hours of parliamentary speech from the European parliament in 23 European
languages.
The entire dataset~\parencite{babu_xlsr_2021} or a 24k-hour 
portion~\parencite{chen_unispeechsat_2021, chen_wavlm_2021} thereof has been used for pre"=training. BBL
consists of 1k hours of conversational telephone speech in 17 African and Asian
languages.

@@

Researchers also evaluate representations for sentiment analysis with the
INTERFACE~\parencite{hozjan_interface_2002} and MOSEI (CMU Multimodal Opinion
Sentiment and Emotion Intensity)~\parencite{zadeh_multimodal_2018} datasets. INTERFACE
is an emotional speech database for Slovenian, English, Spanish, and French,
and contains six emotions: anger, sadness, joy, fear, disgust, and
surprise, plus neutral. MOSEI is comprised of sentence-level sentiment
annotations of 65 hours of YouTube videos
using emotion categories similar to INTERFACE, but replacing joy with
happiness.

In addition, datasets employed to demonstrate the benefit of SSL
representations on various tasks include VCTK \parencite{veaux_cstr_2016} and VoxCeleb1 \parencite{nagrani_voxceleb_2017} for SID/ASV (automatic speaker verification) tasks, FSC (Fluent Speech Commands) \parencite{lugosch_speech_2019} for IC (intent classification), QUESST
(QUESST 2014) \parencite{anguera_quesst2014_2015} for QbE (query by example), LS En-Fr \parencite{kocabiyikoglu_augmenting_2018} and CoVoST-2 \parencite{wang_covost_2020} for ST (speech translation), and ALFFA and OpenSLR-multi for multilingual ASR. The VCTK corpus includes speech
data with 109 English speakers of various accents, each reading out about 400
sentences sampled from newspapers. VoxCeleb1 is an audio-visual dataset
comprised of short YouTube clips containing human speech. It consists of 1251
unique speakers and 352 hours of audio. FSC contains utterances of spoken
English commands that one might use for a smart home or virtual assistant, and
is used to evaluate the performance of a spoken language understanding system.
The QUESST search dataset comprises spoken documents and queries in 6~languages
to measure the capability of models in spotting spoken keywords from documents.
LS En-Fr is a dataset augmenting existing LS monolingual utterances with
corresponding French translations to train and evaluate English-French machine
translators. CoVoST-2 is a multilingual speech translation benchmark based on
CV. It provides data for translating from English into 15 languages and from 21
languages into English, and has a total of 2.9k hours of speech. The ALFFA
project\footnote{\url{http://alffa.imag.fr}} collects speech of African
languages to promote the development of speech technologies in Africa, and
\parencite{kawakami_learning_2020} leverages four African languages collected in the
project for evaluation: Amharic~\parencite{tachbelie_using_2014}, Fongbe~\parencite{laleye_first_2016},
Swahili~\parencite{gelas_developments_2012}, and Wolof~\parencite{gauthier_collecting_2016}.
In the same work~\parencite{kawakami_learning_2020}, the authors
further select 21 phonetically diverse languages from OpenSLR to evaluate the
generalizability of SSL representations across languages. We denote the
collection as OpenSLR-multi below.

@@

As observed in \cref{table:method_data_setting,table:method_data_setting_2}, LS and WSJ are the most commonly used
pre"=training corpora. At the same time, we observe a
growing industry investment in pre"=training with larger datasets, e.g.,
CPC-8k (8k hours) for Bidir-CPC \parencite{kawakami_learning_2020}, LL (60k hours) for
CPC modified~\parencite{riviere_unsupervised_2020}, 
wav2vec 2.0~\parencite{baevski_wav2vec_2020}, and HuBERT~\parencite{hsu_hubert_2021}, Alexa internal
datasets (10k hours) for wav2vec-c~\parencite{sadhu_wav2vecc_2021}, Didi internal
datasets (10k hours) for MPC~\parencite{jiang_improving_2019, jiang_further_2021}, the
combination of Gigaspeech, VP-24k, and LL (94k hours in total) for
UniSpeech-SAT~\parencite{chen_unispeechsat_2021} and WavLM~\parencite{chen_wavlm_2021}, and
the combination of VP-400K, MLS, CV-dataset, VL and BBL (436k hours in total)
for XLS-R~\parencite{babu_xlsr_2021}. We expect this trend to continue with the growth
in available computing power. Most studies focuses on learning representations
for English, whereas Chinese~\parencite{jiang_improving_2019, jiang_further_2021} and
multilinguality~\parencite{kawakami_learning_2020, babu_xlsr_2021} are also gaining
attention. Compared to pre"=training, datasets used for fine"=tuning are more
diverse and cover downstream tasks as varied as ASR, PR, PC, SID, AED,
Sentiment, ST, and LID. For benchmarking training scenarios covering full
supervision as well as limited resources, the amount of labeled examples used for
fine"=tuning also varies from several minutes up to 1k hours. Recent
benchmarks such as SUPERB~\parencite{yang_superb_2021} that consolidate multiple 
downstream tasks have gained attention for evaluating SSL
methodologies~\parencite{chen_unispeechsat_2021, chen_wavlm_2021}. The goal of such benchmarks is
to provide a holistic evaluation of the performance of learned representations; 
we discuss these in detail in \cref{sec:benchmark}. With the increasing
popularity of SSL research, we expect future experiment settings to proliferate
and cover more languages, downstream tasks, and pre"=training/fine"=tuning
datasets.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{paper_review/ls-test-clean-v2.pdf}
\caption[SSL performance for ASR evaluated on
LS \textit{test-clean}.]{SSL performance on ASR WER (vertical axis) evaluated with
LS \textit{test-clean} split. Techniques are sorted based on the number of
model parameters along the horizontal axis. Markers in blue correspond to models initialized with various SSL
techniques and then fine"=tuned using 960, 100, 10, 1 hour(s), and 10 minutes
respectively. The 960-hour training set is the aggregation of
\textit{train-clean-100}, \textit{train-clean-360}, and
\textit{train-other-500} splits. The 100-, 10-, 1-hour, and 10-minute sets
leverage \textit{train-clean-100} or its sampling, except for Bidir-CPC, which
samples 10\% of the training examples from the entire 960-hour corpus. For simplicity,
several SSL techniques are appended with suffixes \textit{B}, \textit{L},
\textit{XL}, or \textit{XXL} indicating the \textit{Base}, \textit{Large},
\textit{X-Large}, or \textit{XX-Large} variants specified in the original
publication. We also compare with baselines including the log mel filterbank (fBANK) and semi"=supervised, self-training
approaches (iterative pseudo labeling (IPL)~\parencite{xu_iterative_2020}, 
slimIPL~\parencite{likhomanenko_slimipl_2021}, noisy student~\parencite{park_improved_2020}). These approaches are visualized in black. Also, note that the current state of the art---conformer XXL + noisy student~\parencite{zhang_pushing_2020}---is a combination of self-training and SSL techniques. Given the
diversity of the listed methods in experiment settings (e.g., pre"=training corpora
and objectives, whether a language model is used in decoding, whether model
parameters are frozen in fine"=tuning), readers should be careful that the superiority
of methods cannot be decided only based on lower WER numbers.}
\label{fig:asr_result_no_limit}
\end{figure*}

\subsection{Benchmark results and discussion} \label{sec:benchmark} 
Given the diversity of datasets and downstream tasks used to evaluate SSL
techniques in the literature, it is infeasible to discuss all 
experiment settings in this survey. Hence, due to their wide adoption for
experiments conducted by studies in both SSL and the speech community in
general, we focus first on ASR on the LS dataset to understand the
efficacy of SSL. We examine SSL techniques which report ASR results on the LS
\textit{test-clean} split, and summarize the published WER in
\cref{fig:asr_result_no_limit}. The ASR models were obtained first by using
unlabeled speech to pre"=train a model with each SSL technique. The model was
then fine"=tuned on labeled data by utilizing a supervised training objective.
Respectively, 960, 100, 10, 1 hour(s), and 10 minutes of labeled LS training data
were used for fine"=tuning, as indicated in different panels of
\cref{fig:asr_result_no_limit} (see
the caption of \cref{fig:asr_result_no_limit} for more details).
Semi"=supervised methods such as self-training, where a model is first trained
on labeled data to annotate unlabeled speech, and then subsequently trained on
combined golden and self-annotated label-speech pairs, are gaining popularity
in the speech community and have yielded competitive results. For comparison, we also
show performance from such methods (iterative pseudo labeling 
(IPL)~\parencite{xu_iterative_2020}, slimIPL~\parencite{likhomanenko_slimipl_2021}, noisy 
student~\parencite{park_improved_2020}), as well as the current state of the art---conformer XXL + noisy
student~\parencite{zhang_pushing_2020}---which augments SSL with various advanced
techniques including self-training. Furthermore, we illustrate in the figure
the performance of a baseline system \parencite{yang_superb_2021} based on log mel filterbank (fBANK), which is one of the most commonly used features designed by domain experts.
As observed in the figure, most SSL techniques outperform fBANK
features, and with the growing investment in model size, better performance is
achieved. The largest ones, such as wav2vec 2.0-L and HuBERT-L/XL, yield competitive results 
when the entire 960-hour of labeled data is used in
training/fine"=tuning. The benefit of SSL, especially models with more parameters
like wav2vec 2.0 and HuBERT, becomes more evident when the labeling resources
become scarce. Compared to popular semi"=supervised methods such as IPL,
slimIPL, and noisy student using 100 hours of labels, wav2vec~2.0 and HuBERT
achieve lower or competitive WERs with 1 hour or even 10 minutes of labeled
examples. The results are highly favorable for low-resource use cases, for instance when
expanding systems to new domains or languages for which large amounts of unlabeled
audio are available, since collecting labels for new conditions is often prohibitively
slow or costly.

@@

\begin{table}[t]
  \centering
  \footnotesize
  \caption{Tasks where the state of the art is models with SSL pre"=training.}
  \label{table:sota_performance}
  \renewcommand*\arraystretch{1.2}
  \begin{tabular}{llllll}  
    \toprule
    Tasks & Dataset & non-SSL & SSL \\
    \midrule
    ASR (WER $\downarrow$) & LS test-clean/other & 2.1/4.0 \parencite{xu_iterative_2020} & 1.4/2.6 \parencite{zhang_pushing_2020} \\ \hline
    IC (Acc $\uparrow$) & FSC & 98.8 \parencite{lugosch_speech_2019} & 99.3\parencite{chen_unispeechsat_2021} \\ \hline
    SID (Acc $\uparrow$) & VoxCeleb1 & 94.8 \parencite{hajibabaei_unified_2018} & 95.5 \parencite{chen_wavlm_2021} \\ \hline
    ASV (EER $\downarrow$) & VoxCeleb1 & 3.1 \parencite{hajavi_siamese_2021} & 2.4 \parencite{wang_finetuned_2021} \\ \hline
    QbE (MTWV $\uparrow$) & QUESST (EN) & 10.6 \parencite{rodriguez-fuentes_gttsehu_2014} & 11.2\parencite{chen_unispeechsat_2021} \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\subsection{Datasets only for pre"=training} 
\Cref{table:datasets} summarizes datasets used for pre"=training SSL techniques
in the literature. These datasets are usually large but with limited or no
labels. LibriLight (LL)~\parencite{kahn_libri-light_2020}, one of these datasets, is
derived from audiobooks that are part of the
LibriVox\footnote{https://librivox.org/ \label{librivox}} project. LL contains
60k hours of spoken English audio tagged with SNR, speaker ID, and genre
descriptions. The speech examples in Audioset~\parencite{gemmeke_audio_2017}, which
consists of over 2M 10-second YouTube video clips human-annotated with 632
audio events, have also been used for pre"=training. Audioset has 2.5k hours
of audio of varying quality, different languages, and sometimes multiple sound
sources. AVSpeech~\parencite{ephrat_looking_2018} is another large-scale audiovisual
dataset used in SSL research, comprising 4.7k hours of clips from a wide
variety of languages. 
Each clip contains a visible face and audible sound originating from a single
speaker without interfering background signals. The 3100-hour audio part of
AVSpeech has been used to learn audio-only 
representations~\parencite{kawakami_learning_2020}. The Fisher corpus~\parencite{cieri_fisher_2004} collects
over 2k hours of conversational telephone speech, 1k hours of which is utilized
for pre"=training~\parencite{jiang_further_2021}. Industrial researchers have also
begun to build large-scale datasets for learning speech representations.
For instance, 10k hours of real-world far-field English voice commands for
self"=supervised pre"=training have been collected at 
Amazon~\parencite{sadhu_wav2vecc_2021}.

In addition to these English and multilingual efforts, researchers have also
collected corpora for pre"=training Chinese speech representations. Didi Dictation
and Didi Call Center~\parencite{jiang_improving_2019, jiang_further_2021} are two
internal datasets containing respectively 10k hours of read speech collected
from mobile dictation application and 10k hours of spontaneous phone calls
between users and customer service staff.

@@

The speech community also utilizes multilingual corpora. These are often
large-scale, which facilitates pre"=training, but are also partially labeled for ASR
evaluation (PC and PR can be enabled via phone-level forced alignment). These
corpora include Common Voice (CV)~\parencite{ardila_common_2020}, Multilingual
LibriSpeech (MLS)~\parencite{pratap_mls_2020}, VoxPopuli 
(VP)~\parencite{wang_voxpopuli_2021}, and BABEL (BBL)~\parencite{gales_speech_2014}. CV is
an open-source, multi-language, growing dataset of voices containing 11k hours
of audio from 76 languages as of the date this review was written (Common Voice
corpus~7.0). Researchers usually use part of this for pre"=training (e.g., 7k
hours/60 languages in \parencite{babu_xlsr_2021} and 430 hours/29 languages in
\parencite{kawakami_learning_2020}) or evaluation. 
MLS derives content from read audiobooks of LibriVox and contains data in eight
European languages for a total of 50k hours of audio. VP comprises a total of 400k
hours of parliamentary speech from the European Parliament in 23 European
languages.
The entire dataset~\parencite{babu_xlsr_2021} or a 24k-hour 
portion~\parencite{chen_unispeechsat_2021, chen_wavlm_2021} thereof has been used for pre"=training. BBL
consists of 1k hours of conversational telephone speech in 17 African and Asian
languages.

@@

Researchers also evaluate representations for sentiment analysis with the
INTERFACE~\parencite{hozjan_interface_2002} and MOSEI (CMU Multimodal Opinion
Sentiment and Emotion Intensity)~\parencite{zadeh_multimodal_2018} datasets. INTERFACE
is an emotional speech database for Slovenian, English, Spanish, and French,
and contains six emotions: anger, sadness, joy, fear, disgust, and
surprise, plus neutral. MOSEI is composed of sentence-level sentiment
annotations of 65 hours of YouTube videos
using emotion categories similar to INTERFACE, but replacing joy with
happiness.

In addition, datasets employed to demonstrate the benefit of SSL
representations on various tasks include VCTK \parencite{veaux_cstr_2016} and VoxCeleb1 \parencite{nagrani_voxceleb_2017} for SID/ASV (automatic speaker verification) tasks, FSC (Fluent Speech Commands) \parencite{lugosch_speech_2019} for IC (intent classification), QUESST
(QUESST 2014) \parencite{anguera_quesst2014_2015} for QbE (query by example), LS En-Fr \parencite{kocabiyikoglu_augmenting_2018} and CoVoST-2 \parencite{wang_covost_2020} for ST (speech translation), and ALFFA and OpenSLR-multi for multilingual ASR. The VCTK corpus includes speech
data with 109 English speakers of various accents, each reading out about 400
sentences sampled from newspapers. VoxCeleb1 is an audiovisual dataset
comprised of short YouTube clips containing human speech. It consists of 1251
unique speakers and 352 hours of audio. FSC contains utterances of spoken
English commands that one might use for a smart home or virtual assistant, and
is used to evaluate the performance of a spoken language understanding system.
The QUESST search dataset comprises spoken documents and queries in 6~languages
to measure the capability of models in spotting spoken keywords from documents.
LS En-Fr is a dataset augmenting existing LS monolingual utterances with
corresponding French translations to train and evaluate English-French machine
translators. CoVoST-2 is a multilingual speech translation benchmark based on
CV. It provides data for translating from English into 15 languages and from 21
languages into English, and has a total of 2.9k hours of speech. The ALFFA
project\footnote{\url{http://alffa.imag.fr}} collects speech of African
languages to promote the development of speech technologies in Africa, and
\parencite{kawakami_learning_2020} leverages four African languages collected in the
project for evaluation: Amharic~\parencite{tachbelie_using_2014}, Fongbe~\parencite{laleye_first_2016},
Swahili~\parencite{gelas_developments_2012}, and Wolof~\parencite{gauthier_collecting_2016}.
In the same work~\parencite{kawakami_learning_2020}, the authors
further select 21 phonetically diverse languages from OpenSLR to evaluate the
generalizability of SSL representations across languages. We denote the
collection as OpenSLR-multi below.

@@

As observed in \cref{table:method_data_setting,table:method_data_setting_2}, LS and WSJ are the most commonly used
pre"=training corpora. At the same time, we observe a
growing industry investment in pre"=training with larger datasets, e.g.,
CPC-8k (8k hours) for Bidir-CPC \parencite{kawakami_learning_2020}, LL (60k hours) for
CPC modified~\parencite{riviere_unsupervised_2020}, 
wav2vec 2.0~\parencite{baevski_wav2vec_2020}, and HuBERT~\parencite{hsu_hubert_2021}, Alexa internal
datasets (10k hours) for wav2vec-c~\parencite{sadhu_wav2vecc_2021}, Didi internal
datasets (10k hours) for MPC~\parencite{jiang_improving_2019, jiang_further_2021}, the
combination of Gigaspeech, VP-24k, and LL (94k hours in total) for
UniSpeech-SAT~\parencite{chen_unispeechsat_2021} and WavLM~\parencite{chen_wavlm_2021}, and
the combination of VP-400K, MLS, CV-dataset, VL and BBL (436k hours in total)
for XLS-R~\parencite{babu_xlsr_2021}. We expect this trend to continue with the growth
in available computing power. Most studies focus on learning representations
for English, whereas Chinese~\parencite{jiang_improving_2019, jiang_further_2021} and
multilingualism~\parencite{kawakami_learning_2020, babu_xlsr_2021} are also gaining
attention. Compared to pre"=training, datasets used for fine"=tuning are more
diverse and cover downstream tasks as varied as ASR, PR, PC, SID, AED,
Sentiment, ST, and LID. For benchmarking training scenarios covering full
supervision as well as limited resources, the amount of labeled examples used for
fine"=tuning also varies from several minutes up to 1k hours. Recent
benchmarks such as SUPERB~\parencite{yang_superb_2021} that consolidate multiple 
downstream tasks have gained attention for evaluating SSL
methodologies~\parencite{chen_unispeechsat_2021, chen_wavlm_2021}. The goal of such benchmarks is
to provide a holistic evaluation of the performance of learned representations; 
we discuss these in detail in \cref{sec:benchmark}. With the increasing
popularity of SSL research, we expect future experiment settings to proliferate
and cover more languages, downstream tasks, and pre"=training/fine"=tuning
datasets.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{paper_review/ls-test-clean-v2.pdf}
\caption[SSL performance for ASR evaluated on
LS \textit{test-clean}.]{SSL performance on ASR WER (vertical axis) evaluated with
LS \textit{test-clean} split. Techniques are sorted based on the number of
model parameters along the horizontal axis. Markers in blue correspond to models initialized with various SSL
techniques and then fine"=tuned using 960, 100, 10, 1 hour(s), and 10 minutes
respectively. The 960-hour training set is the aggregation of
\textit{train-clean-100}, \textit{train-clean-360}, and
\textit{train-other-500} splits. The 100-, 10-, 1-hour, and 10-minute sets
leverage \textit{train-clean-100} or its sampling, except for Bidir-CPC, which
samples 10\% of the training examples from the entire 960-hour corpus. For simplicity,
several SSL techniques are appended with suffixes \textit{B}, \textit{L},
\textit{XL}, or \textit{XXL} indicating the \textit{Base}, \textit{Large},
\textit{X-Large}, or \textit{XX-Large} variants specified in the original
publication. We also compare with baselines including the log Mel filter bank (fBANK) and semi"=supervised, self-training
approaches (iterative pseudo labeling (IPL)~\parencite{xu_iterative_2020}, 
slimIPL~\parencite{likhomanenko_slimipl_2021}, noisy student~\parencite{park_improved_2020}). These approaches are visualized in black. Also, note that the current state of the art---conformer XXL + noisy student~\parencite{zhang_pushing_2020}---is a combination of self-training and SSL techniques. Given the
diversity of the listed methods in experiment settings (e.g., pre"=training corpora
and objectives, whether a language model is used in decoding, whether model
parameters are frozen in fine"=tuning), readers should be careful that the superiority
of methods cannot be decided only based on lower WER numbers.}
\label{fig:asr_result_no_limit}
\end{figure*}

\subsection{Benchmark results and discussion} \label{sec:benchmark} 
Given the diversity of datasets and downstream tasks used to evaluate SSL
techniques in the literature, it is infeasible to discuss all 
experiment settings in this survey. Hence, due to their wide adoption for
experiments conducted by studies in both SSL and the speech community in
general, we focus first on ASR on the LS dataset to understand the
efficacy of SSL. We examine SSL techniques which report ASR results on the LS
\textit{test-clean} split, and summarize the published WER in
\cref{fig:asr_result_no_limit}. The ASR models were obtained first by using
unlabeled speech to pre"=train a model with each SSL technique. The model was
then fine"=tuned on labeled data by utilizing a supervised training objective.
Respectively, 960, 100, 10, 1 hour(s), and 10 minutes of labeled LS training data
were used for fine"=tuning, as indicated in different panels of
\cref{fig:asr_result_no_limit} (see
the caption of \cref{fig:asr_result_no_limit} for more details).
Semi"=supervised methods such as self-training, where a model is first trained
on labeled data to annotate unlabeled speech, and then subsequently trained on
combined golden and self-annotated label-speech pairs, are gaining popularity
in the speech community and have yielded competitive results. For comparison, we also
show performance from such methods (iterative pseudo labeling 
(IPL)~\parencite{xu_iterative_2020}, slimIPL~\parencite{likhomanenko_slimipl_2021}, noisy 
student~\parencite{park_improved_2020}), as well as the current state of the art---conformer XXL + noisy
student~\parencite{zhang_pushing_2020}---which augments SSL with various advanced
techniques including self-training. Furthermore, we illustrate in the figure
the performance of a baseline system \parencite{yang_superb_2021} based on log Mel filter bank (fBANK), which is one of the most commonly used features designed by domain experts.
As observed in the figure, most SSL techniques outperform fBANK
features, and with the growing investment in model size, better performance is
achieved. The largest ones, such as wav2vec 2.0-L and HuBERT-L/XL, yield competitive results 
when the entire 960-hour of labeled data is used in
training/fine"=tuning. The benefit of SSL, especially models with more parameters
like wav2vec 2.0 and HuBERT, becomes more evident when the labeling resources
become scarce. Compared to popular semi"=supervised methods such as IPL,
slimIPL, and noisy student using 100 hours of labels, wav2vec~2.0 and HuBERT
achieve lower or competitive WERs with 1 hour or even 10 minutes of labeled
examples. The results are highly favorable for low-resource use cases, for instance when
expanding systems to new domains or languages for which large amounts of unlabeled
audio are available, since collecting labels for new conditions is often prohibitively
slow or costly.

@@

\begin{table}[t]
  \centering
  \footnotesize
  \caption{Tasks where the state of the art is models with SSL pre"=training.}
  \label{table:sota_performance}
  \renewcommand*\arraystretch{1.2}
  \begin{tabular}{llllll}  
    \toprule
    Tasks & Dataset & non-SSL & SSL \\
    \midrule
    ASR (WER $\downarrow$) & LS test-clean/other & 2.1/4.0 \parencite{xu_iterative_2020} & 1.4/2.6 \parencite{zhang_pushing_2020} \\ \hline
    IC (Acc. $\uparrow$) & FSC & 98.8 \parencite{lugosch_speech_2019} & 99.3\parencite{chen_unispeechsat_2021} \\ \hline
    SID (Acc. $\uparrow$) & VoxCeleb1 & 94.8 \parencite{hajibabaei_unified_2018} & 95.5 \parencite{chen_wavlm_2021} \\ \hline
    ASV (EER $\downarrow$) & VoxCeleb1 & 3.1 \parencite{hajavi_siamese_2021} & 2.4 \parencite{wang_finetuned_2021} \\ \hline
    QbE (MTWV $\uparrow$) & QUESST (EN) & 10.6 \parencite{rodriguez-fuentes_gttsehu_2014} & 11.2\parencite{chen_unispeechsat_2021} \\
    \bottomrule
  \end{tabular}
\end{table}

### 2023-10-14 chapters/paper_review/04b_analysis.tex
Fix many spelling and language errors

In \parencite{pasad_layerwise_2021} wav2vec~2.0 representations were analyzed with
respect to their acoustic-linguistic information content at different
network layers. Three different mechanisms were used for this
purpose. The first of these is canonical correlation analysis (CCA),
which computes similarity scores between two continuous vectors
based on the maximum correlation of their linear projections.  These
can be used to judge the similarity of embeddings at different layers
with each other, with standard acoustic representations such as mel
filterbank features, or word embeddings derived from text. The second
method clusters continuous representation vectors and computes the
discrete mutual information between cluster IDs and phone or word
labels. The third method involves probing tasks: representation
vectors extracted from the network are used to perform simple
downstream tasks, in particular determining whether two acoustic segments
correspond to the same word, and a standard benchmark of 11 word
similarity tasks~\parencite{faruqi_community_2014}. These are mostly used to gauge the
amount of lexical information present in the embeddings.  Using this
battery of tests the authors compared pre"=trained models of varying
sizes as well as models fine"=tuned for ASR. They found that pre"=trained
models show an autoencoder-style behavior, with early layers showing
strong similarity with input features, intermediate layers diverging
more, and final layers reverting back to higher similarity with input
features and early layers. Generally, the earlier layers in wav2vec~2.0 
models encode acoustic information. The next set of layers encodes
phonetic class information, followed by word meaning information,
before reverting back to encoding phonetic/acoustic information. Thus,
extracting representations from the last layers for tasks that require
phonetic or word-related information may not be the best
strategy. Indeed, the authors of \parencite{baevski_unsupervised_2021} show that a
phone classifier trained on each of the 24 frozen layers of a wav2vec~2.0 model
showed the lowest phone error rates
for layers 10--21 and higher error rates for the other layers. 
\parencite{pasad_layerwise_2021} further show that fine"=tuning the pre"=trained model with a
character-level CTC training criterion changes the behavior of the
last layers (especially the final two layers), breaking the
autoencoder-style behavior and focusing the information encoded in the
last layers on orthographic-phonetic and word information.

@@

A similar insight was obtained in \parencite{zhou_comparison_2020}, which compared vq-vae and
vq-wav2vec with respect to their ability to discover phonetic units.
The vq-vae model extracts continuous features from the audio signal; a
quantizer then  maps them into a discrete space, and a decoder is trained to
reconstruct the original audio conditioned on the latent discrete
representation and the past acoustic observations. By contrast, vq-wav2vec
predicts future latent discrete representations based on contextualized
embeddings of past discrete representations, in a CPC-style way. The models
were evaluated according to their ability to discover phonetic units (as
measured by phone recognition error rate on TIMIT, and the ZeroSpeech ABX task
(see \cref{sec:zero} for more details)), and it was found that the predictive vq-wav2vec
model fared better than the autoencoder-like vq-vae model, most likely due to
its superior ability to model temporal dynamics.

@@

It is well known that traditional speech features like MFCCs lack
robustness against environmental effects such as additive noise,
reverberation, accents, etc., that cause differences in the distributions of
speech features.
Do pre"=trained representations offer greater robustness against distributional
shifts? 
One study~\parencite{kawakami_learning_2020} compared pre"=trained
representations from a CPC model against MFCCs and 
found pre"=trained representations to be more robust to mismatches between
training and test data. The 
training data consisted of clean, read speech (LS)
whereas test data consisted of the Switchboard corpus and TED talks. The
distributional shifts here may stem from both the acoustics (microphone, room
reverberation) as well as
lexical effects related to topic and style, as well as differences in speaker
characteristics such as accent. 
Similar problems were also investigated using HuBERT and wav2vec~2.0 models in
\parencite{chang_exploration_2021}.
In \parencite{hsu_robust_2021} domain effects were studied in greater detail using 
datasets from six different domains. In particular, the authors focused on the
usefulness of adding out-of-domain data to pre"=training. The general
conclusions are that pre"=training on more and diverse domains is preferable:
models pre"=trained on more domains performed better than those pre"=trained on
fewer when tested on held-out domains, regardless of which additional
labeled data was used for fine"=tuning. Adding in-domain unlabeled data---if
available---to pre"=training improves performance robustly; however, even
out-of-domain unlabeled data is helpful and closes  66--73\% of the performance
gap between the ideal setting of in-domain labeled data and a competitive
supervised out-of-domain model.

>>>>

In \parencite{pasad_layerwise_2021} wav2vec~2.0 representations were analyzed with
respect to their acoustic-linguistic information content at different
network layers. Three different mechanisms were used for this
purpose. The first of these is canonical correlation analysis (CCA),
which computes similarity scores between two continuous vectors
based on the maximum correlation of their linear projections.  These
can be used to judge the similarity of embeddings at different layers
with each other, with standard acoustic representations such as Mel
filter bank features, or word embeddings derived from text. The second
method clusters continuous representation vectors and computes the
discrete mutual information between cluster IDs and phone or word
labels. The third method involves probing tasks: representation
vectors extracted from the network are used to perform simple
downstream tasks, in particular determining whether two acoustic segments
correspond to the same word, and a standard benchmark of 11 word
similarity tasks~\parencite{faruqi_community_2014}. These are mostly used to gauge the
amount of lexical information present in the embeddings.  Using this
battery of tests the authors compared pre"=trained models of varying
sizes as well as models fine"=tuned for ASR. They found that pre"=trained
models show an autoencoder-like behavior, with early layers showing
strong similarity with input features, intermediate layers diverging
more, and final layers reverting to higher similarity with input
features and early layers. Generally, the earlier layers in wav2vec~2.0 
models encode acoustic information. The next set of layers encodes
phonetic class information, followed by word meaning information,
before reverting to encoding phonetic/acoustic information. Thus,
extracting representations from the last layers for tasks that require
phonetic or word-related information may not be the best
strategy. Indeed, the authors of \parencite{baevski_unsupervised_2021} show that a
phone classifier trained on each of the 24 frozen layers of a wav2vec~2.0 model
showed the lowest phone error rates
for layers 10--21 and higher error rates for the other layers. 
\parencite{pasad_layerwise_2021} further show that fine"=tuning the pre"=trained model with a
character-level CTC training criterion changes the behavior of the
last layers (especially the final two layers), breaking the
autoencoder-like behavior and focusing the information encoded in the
last layers on orthographic-phonetic and word information.

@@

A similar insight was obtained in \parencite{zhou_comparison_2020}, which compared VQ-VAE and
vq-wav2vec with respect to their ability to discover phonetic units.
The VQ-VAE model extracts continuous features from the audio signal; a
quantizer then  maps them into a discrete space, and a decoder is trained to
reconstruct the original audio conditioned on the latent discrete
representation and the past acoustic observations. By contrast, vq-wav2vec
predicts future latent discrete representations based on contextualized
embeddings of past discrete representations, in a CPC-style way. The models
were evaluated according to their ability to discover phonetic units (as
measured by phone recognition error rate on TIMIT, and the ZeroSpeech ABX task
(see \cref{sec:zero} for more details)), and it was found that the predictive vq-wav2vec
model fared better than the autoencoder-like VQ-VAE model, most likely due to
its superior ability to model temporal dynamics.

@@

It is well known that traditional speech features like MFCCs lack
robustness against environmental effects such as additive noise,
reverberation, accents, etc., that cause differences in the distributions of
speech features.
Do pre"=trained representations offer greater robustness against distributional
shifts? 
One study~\parencite{kawakami_learning_2020} compared pre"=trained
representations from a CPC model against MFCCs and 
found pre"=trained representations to be more robust to mismatches between
training and test data. The 
training data consisted of clean, read speech (LS)
whereas test data consisted of the Switchboard corpus and TED talks. The
distributional shifts here may stem from both the acoustics (microphone, room
reverberation),
lexical effects related to topic and style, and differences in speaker
characteristics such as accent. 
Similar problems were also investigated using HuBERT and wav2vec~2.0 models in
\parencite{chang_exploration_2021}.
In \parencite{hsu_robust_2021} domain effects were studied in greater detail using 
datasets from six different domains. In particular, the authors focused on the
usefulness of adding out-of-domain data to pre"=training. The general
conclusions are that pre"=training on more and diverse domains is preferable:
models pre"=trained on more domains performed better than those pre"=trained on
fewer when tested on held-out domains, regardless of which additional
labeled data was used for fine"=tuning. Adding in-domain unlabeled data---if
available---to pre"=training improves performance robustly; however, even
out-of-domain unlabeled data is helpful and closes  66--73\% of the performance
gap between the ideal setting of in-domain labeled data and a competitive
supervised out-of-domain model.
